Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-08 paper/paper.tex
pass on intro

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with significant
penetration in the segments of web development, mobile, and even for
client and server coding for the Internet of
Things~(IoT)~\cite{simply-technologies}.

The interest of the community for the language encourages constant
improvements in its specification and implementations.  It is natural
to expect that language improvements entails sensible implementation
changes. Even small changes can have high impact. For example, in
October 2014 a new attribute added to Array objects caused a bug that
resulted in the web app for the MS Outlook Calendar not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
bugs in JS engines is therefore an important problem given the range
of applications that could be affected. It is also challenging as
specifications evolve constantly and are incomplete. More
specifically, the evolution of the \js\ specification makes it hard to
assess if a test fails because of a bug or because of some missing
feature. The publicly-available Kangax compatibility
table~\cite{kangax} highlights this problem; it relates features with
the engines that (partially) support them. For similar reason, one
could misclassify a test failure as a bug when the failure could be,
in fact, caused by some undefined behavior in the spec. To note that
many of these cases exist as it can be observed by searching for
``implementation-dependent'' in the ES6 spec
document~\cite{ecmas262-spec}.

%% WHAT WE DID
This paper reports the results of a study we conducted to assess
reliability of existing JS engines by leveraging implementation
diversity in two orthogonal ways: test transplantation and
cross-engine differential testing.  \emph{Test transplantation}
evaluates the effects that running \js{} test files from a given
engine have in detecting bugs in other engines. The intuition is that
when a bug is found in some engine a test case is created and added to
the regression suite. Those test inputs often check interesting
scenarios that could reveal bugs in different engine
implementations. \emph{Cross-engine differential testing} evaluates
the bug-finding ability of fuzzing existing
inputs~\cite{fuzz-testing-history} and then comparing the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning}. This approach has not been
popularized, certainly because it is impractical to fully automate--a
number of legitimate reasons exist, other than a bug, for a test
execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

>>>>

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with significant
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible implementation changes. Even small changes can have
high impact. For example, in October 2014 a new attribute added to
Array objects caused a bug in the MS Outlook Calendar web app under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging as specifications are incomplete and evolve
frequently. Consequently, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason. For example, a
test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} highlights this problem--it relates features of
\js\ with the engines that support them. As another example of a
failure that is not caused by a bug, a test that passes in one engine
could legitimately fail in another engines because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}.

%% when a bug is found in some engine a test case is created and added to
%% the regression suite. Those test inputs often check interesting
%% scenarios that could reveal bugs in different engine
%% implementations.

%% WHAT WE DID
The goal of this paper is to assess reliability of popular
\js\ engines. The paper reports the results of a study that evaluates
the effectiveness of two complementary diversity-aware techniques to
find bugs in \js\ engines. \emph{Test transplantation} leverages
diversity of test cases to find bugs. It evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that developers design test cases
differently; hence replaying the test in a different engine may reveal
unanticipated problems. \emph{Cross-engine differential testing}
evaluates the ability of leveraging diversity of engine
implementations to find bugs. More precisely, it fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files\footnote{These files are created with the grammar-based fuzzer
  jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning} as opposed to different builds of the
same engine. This approach has not been
popularized, certainly, because it is still not practical to fully automate--a
number of legitimate reasons exist, other than a bug, for a test
execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.
